SDG contributions

### 2023-09-06 article/article.qmd
include 2019 again
was using an outdated file for total MAG. using the 2021 data I have gives sensible numbers of 2019

# Overall MAG data
paper_cols <- c("id", "rank", "doi", "type", "title_normalised", "title", 
                "unknown1", "year", "date", "publisher", paste0("unknown", 2:11),
                "journal", paste0("unknown", c(13, 14)))

mag_2020_papers <- spark_read_csv(sc, "/tklebel/mag2020/papers.txt",
                                   name = "mag2020_papers",
                                   memory = FALSE,
                                  delimiter = "\\t", header = FALSE,
                                  columns = paper_cols)

@@

# remove 2019-2020 altogether. my MAG copy was still incomplete for 2019
papers <- papers %>% 
  filter(year < 2019)

@@

overall_count <- mag_2020_papers %>% 
  filter(year %in% 2006:2019) %>% 
  count(year, name = "overall_n") %>% 
  collect() %>% 
  mutate(year = as.integer(year))

@@

```{r}
growth_rate_data %>% 
  filter(year %in% c(2006, 2018)) %>% 
  summarise(overall_growth_factor = {overall_n / lag(overall_n)}[2],
            individual_growth_factor = {n / lag(n)}[2],
            individual_growth_rate = individual_growth_factor^(1/(2018-2006)) - 1,
            overall_growth_rate = overall_growth_factor^(1/(2018-2006)) - 1) %>% 
  knitr::kable()

@@

>>>>

# Overall MAG data
paper_cols <- c("id", "rank", "doi", "type", "title_normalised", "title", 
                "unknown1", "year", "date", "unknown2", "publisher", 
                paste0("unknown", 3:12),
                "journal", paste0("unknown", c(14:16)))

mag_2021_papers <- spark_read_csv(sc, "/tklebel/mag-2021-03-15/Papers.txt",
                                  name = "mag2021_papers",
                                  memory = FALSE,
                                  delimiter = "\\t", header = FALSE,
                                  columns = paper_cols)

mag_2021_paper_author_affil <- spark_read_csv(
  sc, 
  "/tklebel/mag-2021-03-15/PaperAuthorAffiliations.txt",
  name = "mag2021_paper_author_affil", delimiter = "\\t",
  memory = FALSE, header = FALSE)

@@

# remove 2020
papers <- papers %>% 
  filter(year < 2020)

@@

overall_count <- mag_2021_papers %>% 
  filter(year %in% 2006:2019) %>% 
  count(year, name = "overall_n") %>% 
  collect() %>% 
  mutate(year = as.integer(year))

@@

```{r}
growth_rate_data %>% 
  filter(year %in% c(2006, 2019)) %>% 
  summarise(overall_growth_factor = {overall_n / lag(overall_n)}[2],
            individual_growth_factor = {n / lag(n)}[2],
            individual_growth_rate = individual_growth_factor^(1/(2019-2006)) - 1,
            overall_growth_rate = overall_growth_factor^(1/(2019-2006)) - 1) %>% 
  knitr::kable()

@@

Need a baseline across all of MAG. For this we need:

- all papers
- all paper author affils
- mapping between affil and country
